Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-09-07 papers/thesis-kirstie/thesis.tex
more modifications and removed a bunch of junk

The Grand free energy is applicable to systems with a varying number of particles and fixed chemical potential, temperature and volume. But this paper will be examining a system with a fixed temperature, volume, and number of particles in which case it is the Helmholtz energy as a functional of the number density profile $F[n(\vec r)]$ that is of interest. 
%*********************** DFT minimize F/N *********************
%--------------------------------------------------------
%\color{red}
%Starting with Euler's equation
%%\begin{equation}U=TS-PV+\mu{N}\end{equation}
%\begin{equation}\frac{U}{N}=\frac{TS}{N}-\frac{PV}{N}+\mu\end{equation}
%\begin{equation}\label{d(U/N)long}d\left(\frac{U}{N}\right)=\frac{T}{N}dS+\frac{S}{N}%dT+TSd\left(\frac{1}{N}\right)-\frac{V}{N}dP-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)%+d\mu\end{equation}
%and using the Gibbs-Duhem relation which follows from Euler's equation
%\begin{equation}SdT-VdP+Nd\mu=0\end{equation}
%which gives
%\begin{equation}\frac{S}{N}dT-\frac{V}{N}dP+d\mu=0\end{equation}
%Equation~\ref{d(U/N)long} becomes
%\begin{equation}\label{d(U/N)}d\left(\frac{U}{N}\right)=\frac{T}{N}dS+TSd\left(\frac{1}{N}\right)-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)\end{equation}
%\begin{equation}dU=TdS+SdT-PdV-VdP+\mu{dN}+Nd\mu\end{equation}
%\color{black}
The Helmholtz free energy F is defined as 
\begin{equation}F=U-TS\end{equation}
\begin{equation}\frac{F}{N}=\frac{U}{N}-\frac{TS}{N}\end{equation}
\begin{equation}\label{usetoshowmin}d\left(\frac{F}{N}\right)=d\left(\frac{U}{N}\right)-d\left(\frac{TS}{N}\right)\end{equation}
\begin{equation}d\left(\frac{F}{N}\right)=d\left(\frac{U}{N}\right)-\frac{T}{N}dS-\frac{S}{N}dT-TS d\left(\frac{1}{N}\right)\end{equation}
Setting $f_N=\frac{F}{N}$ this becomes
\begin{equation}df_N=-\frac{S}{N}dT-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)\end{equation}
This result shows that the natural variables of the Helmholtz free energy per particle $f_N$ are temperature, volume and one over the number of particles, which in turn also holds the number density $n=\frac{V}{N}$ fixed. It is the Helmholtz free energy will be minimized in a system that has a temperature, volume, and number of particles that are fixed.
\begin{equation}f_N(T,V, \frac{1}{N})\mbox{~~~~or~~~~}f_N(T,\frac{V}{N})\end{equation}

@@

More generally, the Helmholtz free energy is the value assumed by U-TS for a system that has a fixed volume, number of particles, and temperature that equals the temperature of the reservoir, or surroundings as it settles spontaneously to equilibrium. Under these conditions, the quantity U-TS settles to a minimum at equilibrium with respect to unconstrained variables, such as the number density profile $n(\vec r)$.
\begin{equation}F=\text{min}_{U}(U_{Not.equilibrium} - TS_{Not.equilibrium}) = U_{equilibrium}-TS_{equilibrium}\end{equation}
An extremum is reached when
\begin{equation}\frac{\partial{F}}{\partial{U}}=0\end{equation}
\color{red} 
\begin{equation}F=\text{min}_{n(\vec{r})}(U_{Not.equilibrium} - TS_{Not.equilibrium}) = U_{equilibrium}-TS_{equilibrium}\end{equation} 
\color{red} 
\begin{equation}\frac{\delta{F}}{\delta{n(\vec r)}}\bigg|_{n(\vec{r})_{equil}}=0\end{equation}
Taking this derivative gives  ??????? CHECK PARTIAL DERVIVATIVE OF FUNCTIONAL 
%\begin{equation}\frac{\partial{(U-TS)}}{\partial{n(\vec r)}}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\frac{\partial{S}}{\partial{U}}\bigg|_{V,N}\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}\frac{\partial{(U-TS)}}{\partial{n(\vec r)}}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\frac{\partial{S}}{\partial{U}}\bigg|_{V,N}\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\left(\frac{1}{T}\right)\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=\frac{\partial{U}}{\partial{n(\vec r)}}-\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=0\end{equation}
\color{black}
As shown earlier, the extremum that is reached at equilibrium is a minimum. (reference shethna) \color{red} To show that there is only one minimum, that the extremum is unique, I refer the reader to ...(reference fluids). \color{black} It remains to be shown that the Helmholtz free energy can be expressed as a functional of the number density profile.

@@

Now consider the excess free energy which is written most generally as
\begin{equation}\label{Fexcess}{F_{excess}= -k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}~e^\frac{-V(\vec{r}_1, \vec{r}_2,...\vec{r}_N)-V_{ext}(\vec{r}_1, \vec{r}_2,...\vec{r}_N)}{k_BT}\right)}}\end{equation} 
This integral can be greatly simplified if it can be assumed that the potential energy $V(\vec{r_1},\vec{r_2},...\vec{r_N})$ is a sum of the potential energies between pairs of atoms, where each atom is paired in turn with each of the other atoms in the system. In this case $V(\vec{r}_1, \vec{r}_2,...\vec{r}_N)$ becomes 
\begin{equation}{V(\vec{r_1},\vec{r_2},...\vec{r_N})=\frac{1}{2}\sum^N_i\sum^N_{j\neq{i}}V_{ij}(\vec{r_i},\vec{r_j})}\end{equation} 
%\begin{displaymath}{=V_{12}(\vec{r_1},\vec{r_2})+V_{13}(\vec{r_1},\vec{r_3}) + V_{14}(\vec{r_1},\vec{r_4}) + ...}\end{displaymath}
%\begin{displaymath}{+ V_{23}(\vec{r_2},\vec{r_3})+V_{24}(\vec{r_2},\vec{r_4})+V_{25}(\vec{r_2},\vec{r_5})+ ...}\end{displaymath} 
%\begin{displaymath}{+ V_{34}(\vec{r_3},\vec{r_4})+V_{35}(\vec{r_3},\vec{r_5})+V_{36}(\vec{r_3},\vec{r_6})+...}\end{displaymath}
Using this potential, and setting the external potential $V_{ext}(\vec{r}_1, \vec{r}_2,...\vec{r}_N)$ to zero, the exponent in Equation~\ref{Fexcess} becomes

\begin{displaymath}{e^{-\frac{\frac{1}{2}\sum^N_i\sum^N_{j\neq{i}}V_{ij}(\vec{r_i},\vec{r_j})}{k_BT}}=e^{\frac{-V_{12}(\vec{r_1},\vec{r_2})}{k_BT}}e^{-\frac{V_{13}(\vec{r_1},\vec{r_3})}{k_BT}}e^{-\frac{V_{14}(\vec{r_1},\vec{r_4})}{k_BT}}...}\end{displaymath}    \begin{equation}{\approx-(1+f_{12})(1+f_{13})(1+f_{14})...}\end{equation}
where each exponential term is simplified by a Taylor expansion $e^x\approx{1+x}$. %\begin{equation}{\exp^{-V_{ij}(\vec{r_i},\vec{r_j})}\approx 1+f_{ij}(\vec{r_i},\vec{r_j})}\end{equation}%    %$\exp^x=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}...$.%  
The function $f_{ij}$ is called a Mayer function, and is given by\begin{equation}{f_{ij}(\vec{r_i},\vec{r_j})=e^{-\frac{V_{ij}(\vec{r_i},\vec{r_j})}{k_BT}}-1}\end{equation} 
Multiplying the Mayer function terms, the excess free energy can be written as
\begin{equation}{F_{excess}=-k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}\left[1 + \sum{f_{ij}} + \sum{f_{ij}f_{kl}} +\sum{f_{ij}f_{kl}f_{mn}} +... \right]\right)  }}\end{equation}
At low densities, it is not likely to find two or more spheres in close proximity, and so only interactions between pairs of spheres are considered. In this case the equation reduces to
%\begin{equation}{F_{excess}=-k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}\left[1 + \sum{f_{ij}} + \sum_{i\neq{j}\neq{k}\neq{l}}{f_{ij}f_{kl}} +\sum_{i\neq{j}\neq{k}\neq{l}\neq{m}\neq{n}}{f_{ij}f_{kl}f_{mn}} +... \right]\right)  }}\end{equation} 
\begin{equation}{F_{excess}=-k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}\left[1 + \sum{f_{ij}} + \sum_{i\neq{j}\neq{k}\neq{l}}{f_{ij}f_{kl}} +... \right]\right)  }}\end{equation} 
Making a change of variables $\vec{r}=\vec{r}_i-\vec{r}_j $ we get \begin{equation}{\int{...}\int{dQ}=V^N}\end{equation}\begin{equation}{\int{...}\int{dQ}\sum{f_{ij}}=\frac{1}{2}N(N-1)V^{N-1}\int{f(r)}{d\vec{r}}}\end{equation} \begin{equation}{\int{...}\int{dQ}\sum{f_{ij}f_{kl}}=\frac{1}{8}N(N-1)(N-2)(N-3)V^{N-2}\int{f(r)}{d\vec{r}}\int{f(r)}{d\vec{r}}}\end{equation} 
%which becomes \begin{equation}{F_{excess}=-k_BT\ln{\left(1+ \frac{1}{2}\frac{N(N-1)}{V^{N}}V^{N-2}\int{...}\int{dQ}{f_{ij}} + .....\sum_{i\neq{j}\neq{k}\neq{l}}{f_{ij}f_{kl}} +\sum_{i\neq{j}\neq{k}\neq{l}\neq{m}\neq{n}}{f_{ij}f_{kl}f_{mn}} +...\right)}}\end{equation}% 
%FINISH!!!!! \begin{equation}{\int{...}\int{dQ}\sum{f_{ij}f_{kl}f_{mn}}=\frac{1}{48}N(N-1)(N-2)(N-3)(N-4)(N-5)(N-6)V^{N-3}\int{f(r)}{d\vec{r}}\int{f(r)}{d\vec{r}}\int{f(r)}{d\vec{r}}}\end{equation} 
and so on. In the low-density limit, the terms in the series get smaller, and the excess free energy can then be written as %begin{equation}{F_{excess}=-k_BT\ln\left(1+\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}+\frac{1}{8}\frac{N^4}{V^{2}}\int{f(r)}{d\vec{r}}\int{f(r)}{d\vec{r}}+ ...\right)}\end{equation}%
\begin{equation}{F_{excess}=-k_BT\ln\left(1+\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}+\frac{1}{2}\left(\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}\right)^2+ ...\right)}\end{equation}
where in the thermodynamic limit (large N), $N-1, N-2, ...\approx{N}$. Written in terms of an exponential $e^x=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+ ...$ for a homogeneous density n=$\frac{N}{V}$ this becomes
\begin{equation}{F_{excess}=-k_BT\ln{\left(e^{\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}}\right)}}\end{equation} \begin{equation}{F_{excess}=-k_BT\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}}\end{equation}  %\begin{equation}{F_{excess}=k_BT\frac{N^2}{V}\left(-\frac{1}{2}\int{f(r)}{d\vec{r}}\right)}\end{equation}%
Thus the free excess energy per atom in the low-density limit is  \begin{equation}{\frac{F_{excess}}{N}=k_BTn\left(-\frac{1}{2}\int{f(r)}{d\vec{r}}\right)}\end{equation} where the quantity in parenthesis can be recognized as the second virial expanision coefficient typically called $B_2$. %where $x=\frac{1}{2}\frac{N(N-1)}{V^{2}}\int{...}\int{dQ}{f_{12}}$.% 
It is important that the expression for the excess Helmholtz free energy correctly reduces to this result in the low-density limit.
%Although we will not be restricting ourselves to the low-density limit, it is important that the theory we use correctly reduces to this same result in the low-density limit.

@@

Another way to form an expression for the excess Helmholtz free energy as a functional of the number density profile $n(\vec r)$ is to use Fundamental Measure Theory (FMT). FMT was developed for hard sphere fluids, and has been very sucessful at predicting the thermodynamic properties of inhomogeneous hard sphere fluids starting from an expression for the excess Helmholtz free energy obtained from Scaled Partical Theory (SPT). Soft Fundamental Measure Theory (SFMT), which will be addressed later, extends FMT to fluids with soft potentials like that of the WCA fluid.

@@

--------------------------------------------------

@@

\item Fourier Transforms of Weight Functions $w_0(r), w_1(r), w_2(r), w_3(r)$
\item Fourier Transforms of Vector Weight Functions $\vec{w}_1(\vec{r}), \vec{w}_2(\vec{r})$  
\item Fourier Transform of Tensor Weight $\overleftrightarrow{w}_{m2}(r)$ in coordinate system (x',y',z')
%\item The tensor weight components in the coordinate system (x,y,z) 
%\item Show transform of tensor weight $\overleftrightarrow{w}_{m2}(r)$ goes to zero as k goes to 0
\item Integrals used to Compute Fourier Transforms of Weight Functions
\item Deriviation of Tensor Density $n_{m2ij}(\vec{r})$ 
\item Deriviation of the Tensor version of $\Phi_3$ 
\item Equations related to the Error Function Potential $V_{erf}$ ....
\item Second Virial Coefficient $B_{2}$ for the Error Function Potential 
\item Third Virial Coefficient $B_{3}$
\end{enumerate}

@@

\textbf{6. Deriviation of $\Phi_3$}

@@

%\textbf{7. Equations related to the Error Function Potential $V_{erf}$ ....:}
%\[{}\]
%\[{}\]

\textbf{8. Second Virial Coefficient $B_{2}$ for the Error Function Potential $V_{erf}$:}
\begin{equation}B_2=-\frac{1}{2}\int_{allspace}f(\vec{r})d\vec r\end{equation}
The mayer function for the Error Function potential $V_{erf}$ is
\begin{equation}f(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation} from which it can be seen that $f(r)$ is approximately 0 for $r>r_{max}$ where $r_{max}$ is some maximum value of $r$.
\begin{align}
 B_2 &= -\frac{1}{2}\int_0^{\pi}\int_0^{2\pi}\int_0^\infty\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2\sin{\theta}d{\theta}d{\phi}dr \\
     &= -\frac{1}{2}4\pi\frac{1}{2}\int_{0}^{r_{max}}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2dr \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \pi\int_0^{r_{max}}r^2dr   \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \frac{\pi}{3}r_{max}^3   
\end{align}

@@

\[{}\]
\textbf{9. Third Virial Coefficient $B_{3}$:}

@@

%-----------------END Virial Expansion---------------
%\[\]

>>>>

The Grand free energy is applicable to systems with a varying number of particles and fixed chemical potential, temperature and volume. But this paper will be examining a system with a fixed temperature, volume, and number of particles in which case it is the Helmholtz energy as a functional of the number density profile $F[n(\vec r)]$ that is of interest. 
%*********************** DFT minimize F/N *********************
%--------------------------------------------------------
%\color{red}
%Starting with Euler's equation
%%\begin{equation}U=TS-PV+\mu{N}\end{equation}
%\begin{equation}\frac{U}{N}=\frac{TS}{N}-\frac{PV}{N}+\mu\end{equation}
%\begin{equation}\label{d(U/N)long}d\left(\frac{U}{N}\right)=\frac{T}{N}dS+\frac{S}{N}%dT+TSd\left(\frac{1}{N}\right)-\frac{V}{N}dP-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)%+d\mu\end{equation}
%and using the Gibbs-Duhem relation which follows from Euler's equation
%\begin{equation}SdT-VdP+Nd\mu=0\end{equation}
%which gives
%\begin{equation}\frac{S}{N}dT-\frac{V}{N}dP+d\mu=0\end{equation}
%Equation~\ref{d(U/N)long} becomes
%\begin{equation}\label{d(U/N)}d\left(\frac{U}{N}\right)=\frac{T}{N}dS+TSd\left(\frac{1}{N}\right)-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)\end{equation}
%\begin{equation}dU=TdS+SdT-PdV-VdP+\mu{dN}+Nd\mu\end{equation}
%\color{black}
The Helmholtz free energy F is defined as 
\begin{equation}F=U-TS\end{equation}
\begin{equation}\frac{F}{N}=\frac{U}{N}-\frac{TS}{N}\end{equation}
\begin{equation}\label{usetoshowmin}d\left(\frac{F}{N}\right)=d\left(\frac{U}{N}\right)-d\left(\frac{TS}{N}\right)\end{equation}
\begin{equation}d\left(\frac{F}{N}\right)=d\left(\frac{U}{N}\right)-\frac{T}{N}dS-\frac{S}{N}dT-TS d\left(\frac{1}{N}\right)\end{equation}
Setting $f_N=\frac{F}{N}$ this becomes
\begin{equation}df_N=-\frac{S}{N}dT-\frac{P}{N}dV-PVd\left(\frac{1}{N}\right)\end{equation}
This result shows that the natural variables of the Helmholtz free energy per particle $f_N$ are temperature, volume and one over the number of particles, which in turn also holds the number density $n=\frac{V}{N}$ fixed. It is the Helmholtz free energy will be minimized in a system that has a temperature, volume, and number of particles that are fixed.
%\begin{equation}f_N(T,V, \frac{1}{N})\mbox{~~~~or~~~~}f_N(T,n)\end{equation}
\begin{equation}f_N(T,V, \frac{1}{N})\end{equation}

@@

More generally, the Helmholtz free energy is the value assumed by U-TS for a system that has a fixed volume, number of particles, and temperature that equals the temperature of the reservoir, or surroundings as it settles spontaneously to equilibrium. Under these conditions, the quantity U-TS settles to a minimum at equilibrium with respect to unconstrained variables, such as the number density profile $n(\vec r)$.
\begin{equation}F=\text{min}_{U}(U_{Not.equilibrium} - TS_{Not.equilibrium}) = U_{equilibrium}-TS_{equilibrium}\end{equation}
An extremum is reached when
\begin{equation}\frac{\partial{F}}{\partial{U}}=0\end{equation}
\color{red} 
\begin{equation}F=\text{min}_{n(\vec{r})}(U_{Not.equilibrium} - TS_{Not.equilibrium}) = U_{equilibrium}-TS_{equilibrium}\end{equation} 
\color{red} 
\begin{equation}\frac{\delta{F}}{\delta{n(\vec r)}}\bigg|_{n(\vec{r})_{equil}}=0\end{equation}
Taking this derivative gives  ??????? CHECK PARTIAL DERVIVATIVE OF FUNCTIONAL 
%\begin{equation}\frac{\partial{(U-TS)}}{\partial{n(\vec r)}}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\frac{\partial{S}}{\partial{U}}\bigg|_{V,N}\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}\frac{\partial{(U-TS)}}{\partial{n(\vec r)}}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\frac{\partial{S}}{\partial{U}}\bigg|_{V,N}\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=\frac{\partial{U}}{\partial{n(\vec r)}}-T\left(\frac{1}{T}\right)\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=\frac{\partial{U}}{\partial{n(\vec r)}}-\frac{\partial{U}}{\partial{n(\vec r)}}\end{equation}
\begin{equation}=0\end{equation}
\color{black}
As shown earlier, the extremum that is reached at equilibrium is a minimum. (reference shethna) %\color{red} To show that there is only one minimum, that the extremum is unique, I refer the reader to ...(reference fluids). \color{black} 
\color{red} To show that F is unique ... \color{black} 
It remains to be shown that the Helmholtz free energy can be expressed as a functional of the number density profile.

@@

Now consider the excess free energy which is written most generally as
\begin{equation}\label{Fexcess-mostgeneral}{F_{excess}= -k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}~e^\frac{-V(\vec{r}_1, \vec{r}_2,...\vec{r}_N)-V_{ext}(\vec{r}_1, \vec{r}_2,...\vec{r}_N)}{k_BT}\right)}}\end{equation} 
This integral can be greatly simplified if it can be assumed that the potential energy $V(\vec{r_1},\vec{r_2},...\vec{r_N})$ is a sum of the potential energies between pairs of atoms, where each atom is paired in turn with each of the other atoms in the system. In this case $V(\vec{r}_1, \vec{r}_2,...\vec{r}_N)$ becomes 
\begin{equation}{V(\vec{r_1},\vec{r_2},...\vec{r_N})=\frac{1}{2}\sum^N_i\sum^N_{j\neq{i}}V_{ij}(\vec{r_i},\vec{r_j})}\end{equation} 
%\begin{displaymath}{=V_{12}(\vec{r_1},\vec{r_2})+V_{13}(\vec{r_1},\vec{r_3}) + V_{14}(\vec{r_1},\vec{r_4}) + ...}\end{displaymath}
%\begin{displaymath}{+ V_{23}(\vec{r_2},\vec{r_3})+V_{24}(\vec{r_2},\vec{r_4})+V_{25}(\vec{r_2},\vec{r_5})+ ...}\end{displaymath} 
%\begin{displaymath}{+ V_{34}(\vec{r_3},\vec{r_4})+V_{35}(\vec{r_3},\vec{r_5})+V_{36}(\vec{r_3},\vec{r_6})+...}\end{displaymath}
Using this potential, and setting the external potential $V_{ext}(\vec{r}_1, \vec{r}_2,...\vec{r}_N)$ to zero, the exponent in Equation~\ref{Fexcess} becomes

\begin{displaymath}{e^{-\frac{\frac{1}{2}\sum^N_i\sum^N_{j\neq{i}}V_{ij}(\vec{r_i},\vec{r_j})}{k_BT}}=e^{\frac{-V_{12}(\vec{r_1},\vec{r_2})}{k_BT}}e^{-\frac{V_{13}(\vec{r_1},\vec{r_3})}{k_BT}}e^{-\frac{V_{14}(\vec{r_1},\vec{r_4})}{k_BT}}...}\end{displaymath}    \begin{equation}{\approx-(1+f_{12})(1+f_{13})(1+f_{14})...}\end{equation}
where each exponential term is simplified by a Taylor expansion $e^x\approx{1+x}$. %\begin{equation}{\exp^{-V_{ij}(\vec{r_i},\vec{r_j})}\approx 1+f_{ij}(\vec{r_i},\vec{r_j})}\end{equation}%    %$\exp^x=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}...$.%  
The function $f_{ij}$ is called a Mayer function, and is given by
\begin{equation}{f_{ij}(\vec{r_i},\vec{r_j})=e^{-\frac{V_{ij}(\vec{r_i},\vec{r_j})}{k_BT}}-1}\end{equation} 
Multiplying the Mayer function terms, the excess free energy can be written as
\begin{equation}\label{Fexcess-simplified}{F_{excess}=-k_BT\ln{\left(\frac{1}{V^N}\int{...}\int{dQ}\left[1 + \sum{f_{ij}} + \sum{f_{ij}f_{kl}} +\sum{f_{ij}f_{kl}f_{mn}} +... \right]\right)  }}\end{equation}

  \begin{figure}[h!]
    \centering
    %\includegraphics[height=7cm]{diagrammic.pdf}
    \caption{Two-pair Interactions $f_{ij}f_{kl}$ for N=4 atoms. Interations between individual pairs of atoms are shown in green. 
             Interactions between pairs of atoms with an atom shared in common are shown in red. 
             At low densities only the interactions shown in green are considered, since atoms are not likely to be clustered.}
    \label{fig:diagrammic}
  \end{figure}

At low densities, it is not likely to find two or more atoms in close proximity, and so only interactions between individual pairs of spheres, such as those shown in green in Figure~\ref{fig:diagrammic}, are considered.
Each pair can then be described by a function of the distance between the two atoms in the pair. Making a change of variables $\vec{r}=\vec{r}_i-\vec{r}_j $ for each pair we get 
\begin{equation}f_{ij}(\vec{r_i}-\vec{r_j})=f(\vec{r})=e^{-\frac{V(\vec{r})}{k_BT}}-1\end{equation} 
\color{black}
With a careful counting of the resulting number of such pairs, the excess free energy can then be written as 
where in the thermodynamic limit (large N), $N-1, N-2, ...\approx{N}$. 
Written in terms of an exponential $e^x=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+ ...$ for a homogeneous density n=$\frac{N}{V}$ this becomes
\begin{equation}{F_{excess}=-k_BT\ln{\left(e^{\frac{1}{2}\frac{N^2}{V}\int{f(r)}{d\vec{r}}}\right)}}\end{equation} 
Thus the free excess energy per atom in the low-density limit is given by 
\begin{equation}{\frac{F_{excess}}{N}=k_BTn\left(-\frac{1}{2}\int{f(r)}{d\vec{r}}\right)}\end{equation} where the quantity in parenthesis can be recognized 
as the second virial expanision coefficient typically called $B_2$. %where $x=\frac{1}{2}\frac{N(N-1)}{V^{2}}\int{...}\int{dQ}{f_{12}}$.% 
It is important that the expression for the excess Helmholtz free energy correctly reduces to this result in the low-density limit. 
%Although we will not be restricting ourselves to the low-density limit, it is important that the theory we use correctly reduces to this same result in the low-density limit. 
Outside of the low density limit, it is quite difficult to evaluate the excess Helmholtz free energy given in Equation~\ref{Fexcess-simplified}. 
Another way to form an expression for the excess Helmholtz free energy in terms of a homogeneous number density is to use Scaled Particle Theory (SPT).

@@

@@

Scaled particle theory seeks a general expression for the excess chemical potential of a homogeneous Hard Sphere fluid 
which can then be integrated to find the excess Helmholtz free energy.
\begin{equation}F_{ex}=\int{\mu_{ex}dN}\end{equation}
It is an extension of the work done by Widom who showed that the excess chemical potential of a homogenesous fluid corredsponds to the reversible work 
of inserting a sphere of radius R into a fluid consisting of hard spheres of radius R.

Widom's result was obtained by considering the difference in the excess Helmholtz free energy when one atom is added to an otherwise closed system. 
He showed that the excess chemcial potential is related to the ensemble average of the Boltzman factor for the potential energy difference $V_{diff}$ 
between a system with N atoms and one with N+1 atoms. The resulting equation is known as Widom's Insertion Formula.
%\begin{displaymath}\mu_{ex}=\frac{\partial{F_{ex}}}{\partial{N}}\bigg|_{T,V}{~~~~~~}\end{displaymath}
\begin{equation}\mu_{ex}=\frac{F_{ex}(N+1)-F_{ex}(N)}{\Delta{N}}\bigg|_{T,V}\end{equation}
\begin{equation}\label{widoms-insertion-formula}{~}=-k_BT\ln\left(<e^{-\beta{V_{diff}}}>\right)\end{equation}
%Equation~\ref{widom} is called Widom's Insertion Formula.

%%COME BACK TO THIS POINT! >>>>>\color{red}For a system... $<e^{-\beta{V_{diff}}}> \rightarrow e^{-\beta{V_{diff}}}$, and Equation~\ref{widoms-insertion-formula} becomes \begin{equation}\mu_{ex}=-k_BT\ln\left(e^{-\beta{V_{diff}}}\right)=-k_BT(-\beta{V}_{diff})=V_{diff}=W_{rev}\end{equation}\color{black}

%In a randomly positioned (I think it has to be homogeneous!)
\noindent To evaluate Equation~\ref{widoms-insertion-formula} for a Hard Sphere fluid consider that
no energy would be required to place a hard sphere at points surrounded by an empty space the size of a hard sphere. 
But a hard sphere cannot be placed at points where a hard sphere would overlap another hard sphere; 
the energy required to do that would be infinite. Thus, for a Hard Sphere fluid, Equation~\ref{widoms-insertion-formula} becomes
\begin{equation}\mu_{ex}=-k_BT\ln\left(P_{NoOverlap}e^{-\beta{V}_{NoOverlap}}+P_{Overlap}e^{-\beta{V}_{Overlap}}\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}e^{-\beta{0}}+P_{Overlap}e^{-\beta\infty}\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}(1)+P_{Overlap}(0)\right)\end{equation}
\begin{equation}=-k_BT\ln\left(P_{NoOverlap}\right)\end{equation}
where $P_{NoOverlap}$ is the probablity of positions existing in the hard fluid that are surrounded by an empty space the size of a hard sphere.

\begin{figure}[h!]
    \centering
    %\includegraphics[height=5cm]{Probability-of-overlap.pdf}
    \caption{No energy is needed to place a sphere at a position where there is no overlap such 
             as shown by the black dot at the center of the dotted region near the top. 
             But it is not possible to place a sphere at a position where an overlap occurs.}
    \label{fig:p_overlap}
  \end{figure}

For a homogeneous system, the probablity of positions existing in the hard fluid that are surrounded 
by an empty space the size of a hard sphere, $P_{NoOverlap}$, can be found by considering 
that $P_{NoOverlap}~=1-~P_{Overlap}$ where $P_{Overlap}$ is simply the number density times the volume of one sphere. 
%\color{red}Thus the chemical potential for a fluid with cavities having a radius equal to the radius R of a hard sphere is \color{black}
\color{red}Thus, for cavities having a radius Ro equal to the radius R of a hard sphere, the chemical potential is found to be \color{black}
%\begin{equation}P_{Overlap}=nV_{sphere}\right)\end{equation}
\begin{equation}\mu_{ex}(Ro=R)=-k_BT\ln\left(1-nV_{sphere}\right)\end{equation}
\color{red} ???More generally, for Ro $<$ R this becomes???
\begin{equation}???\mu_{ex}(Ro < R)=-k_BT(\ln(1-n\frac{4\pi}{3}(R_o+R)^3))???\end{equation}
\color{black}

NOW DO UPPER LIMIT  Ro $>>$ R

For Ro $>>$ R ...

--------------------------------------------------
%-----SFMT -------

An expression for the excess Helmholtz free energy as a functional of the number density profile $n(\vec r)$ can be found using Fundamental Measure Theory (FMT).
FMT was developed for hard sphere fluids, and has been very sucessful at predicting the thermodynamic properties of 
inhomogeneous hard sphere fluids starting from an expression for the excess Helmholtz free energy obtained from Scaled Partical Theory (SPT). 
Soft Fundamental Measure Theory (SFMT), which will be addressed later, extends FMT to fluids with soft potentials like that of the WCA fluid.

@@

\item Fourier Transforms of Weight Functions $w_0(r), w_1(r), w_2(r), w_3(r)$
\item Fourier Transforms of Vector Weight Functions $\vec{w}_1(\vec{r}), \vec{w}_2(\vec{r})$  
\item Fourier Transform of Tensor Weight $\overleftrightarrow{w}_{m2}(r)$ in coordinate system (x',y',z')
%\item The tensor weight components in the coordinate system (x,y,z) 
%\item Show transform of tensor weight $\overleftrightarrow{w}_{m2}(r)$ goes to zero as k goes to 0
\item Integrals used to Compute Fourier Transforms of Weight Functions
\item Deriviation of Tensor Density $n_{m2ij}(\vec{r})$ 
\item Deriviation of the Tensor version of $\Phi_3$ 
\item Second Virial Coefficient $B_{2}$ for the Error Function Potential 
\item Third Virial Coefficient $B_{3}$
\item Derivation of the Virial Equation
\end{enumerate}

@@

\textbf{6. Deriviation of the Tensor version of $\Phi_3$ }

@@

\textbf{7. Second Virial Coefficient $B_{2}$ for the Error Function Potential $V_{erf}$:}
\begin{equation}B_2=-\frac{1}{2}\int_{allspace}f(\vec{r})d\vec r\end{equation}
The mayer function for the Error Function potential $V_{erf}$ is
\begin{equation}f(r)=\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]\end{equation} from which it can be seen that $f(r)$ is approximately 0 for $r>r_{max}$ where $r_{max}$ is some maximum value of $r$.
\begin{align}
 B_2 &= -\frac{1}{2}\int_0^{\pi}\int_0^{2\pi}\int_0^\infty\frac{1}{2}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2\sin{\theta}d{\theta}d{\phi}dr \\
     &= -\frac{1}{2}4\pi\frac{1}{2}\int_{0}^{r_{max}}\left[\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)-1\right]r^2dr \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \pi\int_0^{r_{max}}r^2dr   \\
     &= -\pi\int_{0}^{r_{max}}\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)r^2dr {~~}+{~~} \frac{\pi}{3}r_{max}^3   
\end{align}

@@

\[{}\]
\textbf{8. Third Virial Coefficient $B_{3}$:}

@@

\[{}\]
\noindent \textbf{10. Derivation of the Excess Free Energy from Scaled Particle Theory}

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=3cm]{Probability-of-overlap.pdf}
    \caption{No energy is needed to place a sphere at a position where there is no overlap such 
             as shown by the black dot at the center of the dotted region near the top. 
             But it is not possible to place a sphere at a position where an overlap occurs.}
    \label{fig:p_overlap}
  \end{figure}
